14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
Rules: Update incremental track.

\todo{Update accordingly: Do we run only up to the first unknown status
check-sat or further?}
The incremental track evaluates SMT solvers when interacting with an
external verification framework, e.g., a model checker. This
interaction, ideally, happens by means of an online communication
between the framework and the solver: the framework repeatedly sends
queries to the SMT solver, which in turn answers either \texttt{sat}
or \texttt{unsat}.  In this interaction an SMT solver is required to
accept queries incrementally via its \emph{standard input channel}.

In order to facilitate the evaluation of solvers in this track, we
will set up a ``simulation'' of the aforementioned interaction.  Each
benchmark in the incremental track represents a realistic
communication trace, containing multiple \akey{check-sat} commands
(possibly with corresponding \akey{push 1} and \akey{pop 1} commands),
which is parsed by a \emph{trace executor}. The trace executor serves
the following purposes:
\begin{itemize}
\item it simulates the online interaction by sending single queries to
  the SMT solver (through stdin);
\item it prevents ``look-ahead'' behaviors of SMT solvers;
\item it records time and answers for each command;
\item it guarantees a fair execution for all solvers by abstracting
  from any possible crash, misbehavior, etc.\ that might happen in the
  verification framework.
\end{itemize}
%
The trace executor terminates processing the benchmark script upon
receiving an incorrect response from the solver.

@@

\header{\main Track: Removal of Disagreements.}
%
Before division scores are computed for the \main Track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its parallel performance (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).

>>>>

The incremental track evaluates SMT solvers when interacting with an
external verification framework, e.g., a model checker. This
interaction, ideally, happens by means of an online communication
between the framework and the solver: the framework repeatedly sends
queries to the SMT solver, which in turn answers either \texttt{sat}
or \texttt{unsat}.  In this interaction an SMT solver is required to
accept queries incrementally via its \emph{standard input channel}.

In order to facilitate the evaluation of solvers in this track, we will set up
a ``simulation'' of the aforementioned interaction.  Each benchmark represents
a realistic communication trace, containing multiple \akey{check-sat} commands
(possibly with corresponding \akey{push 1} and \akey{pop 1} commands). It is
parsed by a (publicly available) \emph{trace executor}\footnote{\todo{link}},
which serves the following purposes: \begin{itemize} \item it simulates the
online interaction by sending single queries to the SMT solver (through stdin);
\item it prevents ``look-ahead'' behaviors of SMT solvers;
\item it records time and answers for each command;
\item it guarantees a fair execution for all solvers by abstracting
  from any possible crash, misbehavior, etc.\ that might happen in the
  verification framework.
\end{itemize}

@@

\header{\main and \challenge Track: Removal of Disagreements.}
%
\todo{do we need to update this notion?}
Before division scores are computed for the \main and \challenge tracks,
benchmarks with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status disagree on
their result.  More specifically, a solver (including a solver that was entered
into the competition by the organizers for comparison purposes) is \emph{sound
on benchmarks with known status} for a division if its parallel performance
(Section~\ref{sec:benchmark-scoring}) is of the form $\langle 0, n, w,
c\rangle$ for each benchmark in the division, i.e., if it did not produce any
erroneous results.  Two solvers \emph{disagree} on a benchmark if one of them
reported \texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division scores
(but the organizers may report disagreements for informational purposes).

\header{\incremental Track: Removal of Disagreements.}
\todo{}

\header{\challenge Track: Removal of Disagreements.}
\todo{}
